### 2021-10-21 chapters/testing/environement.tex
draft. first chapter

\section{Empirical Evaluation Protocol}

This thesis is based on the empirical analyses to measure the energy consumption. As we mentioned earlier, we have chosen the \emph{agile} methode. so basically we will reduce the energy consumption with trial and error.

%%%%%%%%% preliminary taughts and section structure 
% The need of reproducibility in our field - software optimization based on empirical studies -

% The importance of Virtualisation for reproducibility \cite{howe_virtual_2012}
% some of the most important parts are
% - fewer constraints on research methods
% - on-demand backups
% - virtual Machines as Publications
% - more Variables captured
\subsection{Threats and Challenges}

One of the most challenges which face the reaserchers is the reproducibility of their tests.Actually many results are not reproducible \footnote{Trouble at the lab, The Economist, 19 October 2013;  www.economist.com/news/briefing/ 21588057-scientists-think-science-self-correcting- alarming-degree-it-not-trouble.}, which let to a \emph{replication crisis}.When this crisis hit most of the empirical studies,most of the reviews now includes reproducibility as one of the minimal standard for judging scientific \cite{peng2011reproducible}. one of the creterions for a reproducidibility is the publication of the dataset and the algorithm run on the raw data to condlude the results. There is even some disagreement about what the terms "reproducibility" or "replicability" by themselves mean \cite{goodman2016does} .According to \cite{echtler2018open} \emph{replicability} extends \emph{reproducibility} to the ability to collect a new raw dataset comparable to the original one by reexecuting the experiment under similar condition, Instead of just the ability to get the same results by ruruning the statistical analyses on the orginal data set.

One major problem that hinders the reproducibility of the empirical tests is the interaction with the external environment, either as concurency or dependencies. Therefore testers won't have the same results unless they duplicate the same environment.
% introduction of vms 
\subsection{Virtualisation}
To resolve this problem, practitioners tend to use Virtualisation. Using virtual machines aka VM gives reaserchers the freedom to choose their own tools, software and operating system that they are the most confortable with without paying the price to change the actual working environment, which will give them eventually more controle over the dependencies and the execution environement. Moreover, using a vm will solve the \emph{replication crisis} thanks to the virtual images, even the most complex architecture can be reproduced easily by just instantiating a copy of the image. Since the virtual machines are agnostic to the host architecture, reaserchers won't have to worry about where and how their experiments are replicated because they have already setup the execution environement. Another advantage to the virtual machines is the snapshot mechanism, it allows reaserchers to create backups and revert some changes with simple clicks. Last but not least,thanks to the isolation, virtual machines push the reproducibility further by allowing the future usages to see all the variables -controled and uncontroled-  and do other analysis without dealing with any dependencies. In his paper \cite{howe_virtual_2012} bill howe lists the advantages of using virtual machines in reaserchers experements including the economical impact and cultural limitation to a such approach.

@@

\begin{figure}
    \center{\includegraphics[width=1\linewidth]{imgs/virtualization_techniques}}
    \caption{Different Methods of Virtualzation}\label{reproducibility:virtualization_technique}
\end{figure}

@@

Figure \ref{reproducibility:virtualization_technique} explains the differents in architecture between the clasic types2 of Virtualisation and Containers.
\begin{itemize}
    \item Type 1: runs directly on the hardware, it is mainly used by the cloud providers where there is no main OS, but just virtaul machines, we can site for this the open-srouce XEN and VMware ESX
    \item Type 2: runs over the hostmachine Operating System, mostly used for personal comptuers, VMware server and virtualBox are famous examples of this type, most of the reaserchers expermentation are run witht this type, howerver due to the 2 Operatings syestms the applications tend to be more slower
    \item containers : Instead of its own kernel, containers used the hots kernel to run their Os, which makes them ligher, quickers and use the full pontial use of the hardware. For this we can cite \emph{Docker}, \emph{Linux LXC}\emph{LXD} \cite{abuabdo_virtualization_2019}
\end{itemize}
\note{Rephrase so i include it before VMs+ add links to the technologies }

\subsection{Docker vs Virtual Machine}
Depsite that Type 1 is more performant than type 2, the second one is the most used in reaserch, since most researchers conducts their experements in their own machine. In the other hand, docker is the most famous thechonology for for containers,

%%%%% THINGS TO ADD : 
% the impact of docker on the reprodudicibility 
% Limits of docker 
% The docker files and the clarification of the methodology

\subsection{Docker and energy}
%  basically just rephrase the paper

\subsection{docker and accuracy}

\subsection{Testing Protocol}
the results of this protocil can be found in the project of the continious integrtation that was made by the intern Mamadou to give a feedback about the evolution of the energyconsumption within time

>>>>

% introduction of vms 
\subsection{Virtualisation}
To resolve this problem, practitioners tend to use Virtualisation. Using virtual machines aka VM gives reaserchers the freedom to choose their own tools, software and operating system that they are the most confortable with without paying the price to change the actual working environment, which will give them eventually more controle over the dependencies and the execution environement. Moreover, using a vm will solve the \emph{replication crisis} thanks to the virtual images, even the most complex architecture can be reproduced easily by just instantiating a copy of the image. Since the virtual machines are agnostic to the host architecture, reaserchers won't have to worry about where and how their experiments are replicated because they have already setup the execution environement. Another advantage to the virtual machines is the snapshot mechanism, it allows reaserchers to create backups and revert some changes with simple clicks. Last but not least,thanks to the isolation, virtual machines push the reproducibility further by allowing the future usages to see all the variables -controled and uncontroled-  and do other analysis without dealing with any dependencies. In his paper \cite{howe_virtual_2012} bill howe lists the advantages of using virtual machines in reaserchers experements including the economical impact and cultural limitation to a such approach.

@@

\begin{figure}
    \center{\includegraphics[width=1\linewidth]{imgs/virtualization_techniques}}
    \caption{Different Methods of Virtualzation}\label{environement:virtualization_technique}
\end{figure}

@@

Figure \ref{environement:virtualization_technique} explains the differents in architecture between the clasic types2 of Virtualisation and Containers.
\begin{itemize}
    \item Type 1: runs directly on the hardware, it is mainly used by the cloud providers where there is no main OS, but just virtaul machines, we can site for this the open-srouce XEN and VMware ESX
    \item Type 2: runs over the hostmachine Operating System, mostly used for personal comptuers, VMware server and virtualBox are famous examples of this type, most of the reaserchers expermentation are run witht this type, howerver due to the 2 Operatings syestms the applications tend to be more slower
    \item containers : Instead of its own kernel, containers used the hots kernel to run their Os, which makes them ligher, quickers and use the full pontial use of the hardware. For this we can cite \emph{Docker}, \emph{Linux LXC}\emph{LXD} \cite{abuabdo_virtualization_2019}
\end{itemize}
%  TODO Rephrase so i include it before VMs+ add links to the technologie

\subsection{Docker vs Virtual Machine}
Depsite that Type 1 is more performant than type 2, the second one is the most used in reaserch, since most researchers conducts their experements in their own machine. In the other hand, docker is the most famous thechonology for for containers.
In ower case we are more prone to docker for two reasons.
\begin{enumerate}
    \item we need a litetweight orchestrator to not affect the energy consumption of ower tests. As prior work mentioned [cite Morabito (2015) and van Kessel et al. (2016)]
          % cite Power efficiency of hypervisor-based virtuali- zation versus container-based virtualization. University of Amsterdam.
    \item since we are using the hardware itself to measure the energy consumption, we are required to interract with the host OS itself.
\end{enumerate}
Special notice to \href{https://github.com/powerapi-ng/virtualwatts}{virtualwatts}. A framework that allows us to retireve the energy consumption of a virtual machine.
%%%%% THINGS TO ADD : 
%% -------------- Dont think so 
% the impact of docker on the reprodudicibility 
% Limits of docker 
% The docker files and the clarification of the methodology 
\subsection{Docker and energy}
Now that we have chosen to go with the containers technorolgy to encapsulate our tests. What would be the impact of this solution on the energy consumption of our tests.

Based on the studies of \cite{eddie_antonio_santos_how_nodate}, who analysed the impact of adding the docker layer on the energy consumption.
In their experement. Eddie Antonio et al run multiple benchmarks with and without docker. and compared their energy consumption and execution time.
The first step was to see the impact of docker deamon while there is no work. to see the impact of the orchestrator alone. Later they had the experiment with the following benchmarks
\begin{itemize}
    \item wordpress
    \item reddis
    \item postfresSQL
\end{itemize}
The following figures represents the energy consumption of the system while it is idle. As we can see  in figure \ref{fig:docker_idle} Docker braught arround 1000joules overhead.
\begin{figure}
    \center{\includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/idle_energy}}
    \caption{energy consumption of Idle system with and without docker \cite{eddie_antonio_santos_how_nodate}}\label{fig:docker_idle}
\end{figure}
In the other hand as we can see in figure \ref{fig:docker_reddis}. docker increased the execution time of the benchmark by 50 seconds which caused an increase in energy since they are highly correlated.
The authors also highlated the fact that this increase of energy consumption is due to the docker deamon and not the fact that the application is in a container. Moreover they estimted the price of this extra energy and it was less than 0.15\$ in the worst case. Which is non significant compared to the advantages that docker bring for isolation and reproducibility.\\
if we  recap this study in one sentence,it would be the following one.
The dockerised softwares tend to consume more energy, because mainly they take more time to be executed.
The average power consumption is higher with only \textbf{2Watts} and it is due to the docker deamon.This overhead can be up to 5\% for IO intensive application, but it is mearly noticiable when it comes to CPU or DRMA intesive works

\begin{figure}
    \includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/reddis_time}
    \includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/reddis_energy}
    \caption{execution time and energy consumption of Redis  with and without docker \cite{eddie_antonio_santos_how_nodate}}\label{fig:docker_reddis}
\end{figure}

%  basically just rephrase the paper

\subsection{docker and accuracy}
%% TODO : add an introduction, maybe some more details 
And now Since the stat of the art has aggreed on the impact of docker on the energy consumption,Let's discuss it's impact on the accuracy. In other words\\
\textbf{RQ :} does Docker affect the energy variation of the exepements ?

To Answer this question we have conducted a preliminary experiment by running the same benchmarks \textsf{LU}, \textsf{CG} and \textsf{EP} in a Docker container and a flat binary format on 3 nodes of the cluster \textsf{Dahu} to assess if Docker induces an additional variation.
Figure~\ref{fig:docker} reports that this is not the case, as the energy consumption variation does not get noticeably affected by Docker while running a same compiled version of the benchmarks at 5\,\%, 50\,\% and 100\,\% workloads.
In fact, while Docker increases the energy consumption due to the extra layer it implements~\cite{eddie_antonio_santos_how}, it does not noticeably affect the energy variation.
The \emph{standard deviation} (STD) is even slightly smaller ($STD_{Docker}=192 mJ$,$STD_{Binary}=207 mJ$), taking into account the measurements errors and the OS activity.

\begin{figure}
    \center{\includegraphics[width=.9\linewidth]{imgs/docvsbin}}
    \caption{Comparing the variation of binary and Docker versions of aggregated \textsf{LU}, \textsf{CG} and \textsf{EP} benchmarks}\label{fig:docker}
\end{figure}
